Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
kill orphans

These environments are not meant perfectly to replicate the network environment
in any particular country.  Censorship environments in are complex and volatile, making
the task of replicating a network environment infeasible. More importantly, replicating these
environments is not critical to this experiment. What is required for this experiment are 
environments which would require users to complete similar Tor configuration 
tasks before they are able to circumvent the censorship environment. We set up the following 
abstract simulations which are inspired by reality and require users to complete various tasks
to circumvent censorship.

@@

All participants will be given the same set of tasks, regardless of their simulated
censorship environment.  Although every participant will attempt to complete the same 
set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
Depending on the censorship environment, some tasks may not even require the use or Tor Browser.

@@

The goal of this experiment is to measure how usable Tor Browser is as a censorship circumvention
tool. We hope that this experiment will provide insight into what usability improvements can be made 
in order to better to make Tor Browser's advanced features more accessible to the average user. The results
of this experiment can be used to inform user interaction designs which will result in shorter configuration
completion time and more reliable communication of the technical task to be completed, all while the 
this experience does not frustrate users from future use. We believe that experiments which perform
iterative A/B testing on various designs in order to increase usability to a wide, anonymous, international 
use base will be an interesting area of user interface design research while also making impacting changes
to a widely used censorship circumvention technology.

@@

\subsection{Usability and Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective.  Clark \etal also provided guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction: Tor works may be difficult for users to understand, 
so familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

@@

After the calibration task, we asked participants to complete
the following Tor Browser--related tasks:

>>>>

These environments are not meant to replicate the network environment
in a particular country.  Censorship environments in are complex and volatile, making
it infeasible to replicating a network precisely. Moreover, precise
environments is not critical to this experiment but rather
environments which would require users to complete similar Tor configuration 
tasks before they are able to circumvent the censorship environment. We set up the following 
abstract environments, which are inspired by reality.

@@

All participants will be given the same set of tasks, regardless of their environment.  
Although every participant will attempt to complete the same 
set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
Depending on the censorship environment, some tasks may not even require the use or Tor Browser.

@@

We hope that this experiment will provide insight into what usability improvements can be made 
in order to better to make Tor Browser's advanced features more accessible to the average user. The results
of this experiment can be used to inform user interaction designs which will result in shorter configuration
completion time and more reliable communication of the technical task to be completed, all while the 
this experience does not frustrate users from future use. We believe that experiments which perform
iterative A/B testing on various designs in order to increase usability to a wide, anonymous, international 
use base will be an interesting area of user interface design research while also making impacting changes
to a widely used censorship circumvention technology.

@@

\subsection{Usability and Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective.  Clark \etal also provided guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

@@

After the calibration task, we asked participants to complete
the following Tor Browser--related tasks: \\
